Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-05-16 README.qmd
Stop using profiles; use pandoc extension modifiers!
Use pandoc extension modifiers to make different versions of the PDFs instead of profiles (https://github.com/quarto-dev/quarto-cli/issues/7371)
Use new manuscript target name

manuscript_target <- targets::tar_read(manuscript_nice)

@@

We use the [**renv** package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of packages, and we use the [**targets** package](https://docs.ropensci.org/targets/) to manage all file dependencies and run the analysis. ([See this for a short helpful walkthrough of **targets**.](https://books.ropensci.org/targets/walkthrough.html)).

@@

1. Download and install these fonts (if you’re using Windows, make sure you right click on the font files and choose “Install for all users” when installing these fonts):
    - [Noto Sans](https://fonts.google.com/specimen/Noto+Sans)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
    - If you’re using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
3. Open `mountainous-mackerel.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. In the terminal, run `quarto install tinytex` to ensure that you have a working LaTeX installation.
5. If it's not installed already, R *should* try to install the **renv** package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.

@@

1. All project data in `data/`
2. An analysis notebook website in `_site/`
3. PDF, HTML, and Word versions of the manuscript in `manuscript/output/` and `manuscript/output-ms`

@@

Because project titles change all the time with revisions, rewriting, and peer review, we used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.

>>>>

manuscript_target <- targets::tar_read(manuscript)

@@

We use the [{renv} package](https://rstudio.github.io/renv/articles/renv.html) to create a stable version-specific library of packages, and we use the [{targets} package](https://docs.ropensci.org/targets/) to manage all file dependencies and run the analysis. ([See this for a short helpful walkthrough of {targets}.](https://books.ropensci.org/targets/walkthrough.html)).

@@

1. Download and install these fonts (if you’re using Windows, make sure you right click on the font files and choose “Install for all users” when installing these fonts):
    - [Noto Sans](https://fonts.google.com/specimen/Noto+Sans)
    - [Linux Libertine O](https://www.cufonfonts.com/font/linux-libertine-o) (also [here](https://sourceforge.net/projects/linuxlibertine/))
    - [Libertinus Math](https://github.com/alerque/libertinus)
2. [Install R](https://cloud.r-project.org/) (and preferably [RStudio](https://www.rstudio.com/products/rstudio/download/#download)).
    - If you're using macOS, [install XQuartz too](https://www.xquartz.org/), so that you have access to the Cairo graphics library
    - If you’re using Windows, [install RTools too](https://cran.r-project.org/bin/windows/Rtools/) and add it to your PATH so that you can install packages from source if needed
3. Open `mountainous-mackerel.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
4. In the terminal, run `quarto install tinytex` to ensure that you have a working LaTeX installation.
5. If it's not installed already, R *should* try to install the {renv} package when you open the RStudio Project for the first time. If you don't see a message about package installation, install it yourself by running `install.packages("renv")` in the R console.
6. Run `renv::restore()` in the R console to install all the required packages for this project.
7. Run `targets::tar_make()` in the R console to automatically download all data files, process the data, run the analysis, and compile the paper and appendix.

@@

1. All project data in `data/`
2. An analysis notebook website in `_site/`
3. PDF, HTML, and Word versions of the manuscript in `manuscript/output/`

@@

Because project titles change all the time with revisions, rewriting, and peer review, we used [{codename}](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-us project name that won't change.
